Draft Manuscript

### 2022-09-23 Prereg_and_manuscript/manuscript.Rmd
data analysis - created facet wrap for all species in one plot, removed regression analysis. Data- adding processed data to the repository

```{#{r table_01, message=FALSE, warning=FALSE, include=FALSE, paged.print=TRUE}

# without the "hold_position" the table ends up at the top of the page
```

@@

```{#{r file="../scripts/figure_03.R"}
# this code chunk calls an external script to generate the plot. If you
# want to load or run code not for a plot you could also use the following.
# Note that it does not seem to work for plots.
# source("../scripts/figure_03.R", local = knitr::knit_global())
```

>>>>

\`\`\`{#{r table_01, message=FALSE, warning=FALSE, include=FALSE, paged.print=TRUE}

# without the "hold_position" the table ends up at the top of the page

@@

`{#{r file="../scripts/figure_03.R"} # this code chunk calls an external script to generate the plot. If you # want to load or run code not for a plot you could also use the following. # Note that it does not seem to work for plots. # source("../scripts/figure_03.R", local = knitr::knit_global())`
